wgcna

### 2019-08-26 analysis/08_wgcna.Rmd
now with hypothesis groups

source("08_WGCNA_1.R")
```

@@

subsetWGCNA(whichgroups = c("female.gonad", "female.hypothalamus", "female.pituitary",
                           "male.gonad", "male.hypothalamus", "male.pituitary"),
            mytitle = "Characterization dendrogram with trait heatmap")
```

@@

```{r wgcna-female, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(whichgroups = c("female.gonad", "female.hypothalamus", "female.pituitary"),
            mytitle = "Female sample dendrogram with trait heatmap")
```

@@

```{r wgcna-male, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("male.gonad", "male.hypothalamus", "male.pituitary"),
            mytitle = "Male sample dendrogram with trait heatmap")
```

@@

>>>>

source("08_WGCNA_1.R")

```

@@

subsetWGCNA(whichgroups = c("female.gonad", "female.hypothalamus", "female.pituitary",
                           "male.gonad", "male.hypothalamus", "male.pituitary"),
            mytitle = "Characterization dendrogram with trait heatmap")

```

@@

```{r wgcna-female, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(whichgroups = c("female.gonad", "female.hypothalamus", "female.pituitary"),
            mytitle = "Female sample dendrogram with trait heatmap")

```

@@

```{r wgcna-male, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("male.gonad", "male.hypothalamus", "male.pituitary"),
            mytitle = "Male sample dendrogram with trait heatmap")

```

@@

## female hypothalamus

```{r wgcna-f-hyp, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("female.hypothalamus"),
            mytitle = "Female hypothalamus sample dendrogram")
```

## female gonad

```{r wgcna-f-gon, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("female.gonad"),
            mytitle = "Female gonad sample dendrogram")
```
